From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-10-01 paper.tex
Typos

\usepackage{xspace}
\newcommand{\eg}{\textit{e.g.}\xspace}
\newcommand{\etal}{\textit{et al.}\xspace}
\newcommand{\ie}{\textit{i.e.}\xspace}
\newcommand{\etc}{\textit{etc.}\xspace}
\newcommand{\vs}{\textit{vs.}\xspace}
\newcommand{\redacted}{\textit{\sc [REDACTED FOR REVIEW]}\xspace}

@@

\title{From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction}

%\author{Séverin Lemaignan \qquad Fernando Garcia \qquad Alexis Jacq \qquad Pierre Dillenbourg\\Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)\\École Polytechnique Fédérale de Lausanne (EPFL)}
\author{Redacted for double-blind review}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{head_pose}
    \caption{The 6D head pose is estimated by fitting a 3D model of an
        adult head (left) {\it\sc[FACE REDACTED FOR REVIEW]} onto the detected 2D features of the face (right). We
        rely on an iterative $PnP$ algorithm, using 8 correspondence pairs
        (three are depicted: the sellion -- the nasal depression --, the left
        tragion and the menton). The 3D origin of the head is set at the sellion.}

@@

The experiment, part of the \redacted project, involves a robot
which tries to engage a child in handwriting tasks using a \emph{learning by
teaching} paradigm (\ie the child is the teacher, and he/she attempts to improve
the robot's handwriting). A tactile tablet is used as writing support.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\columnwidth]{realSetup}
    \caption{\small Picture of the interaction with one of the children
    {\it\sc[FACE REDACTED FOR REVIEW]}.}
    \label{fig:realSetup}
\end{figure}

@@

The interaction is organized in rounds of writing: during a typical round, the
child requests the robot to write something (a single letter, a number, or a
full word), and presents a tactile tablet (equipped with a custom writing
application) to the robot. The robot writes on the tablet by mimicking the
writing gesture (but without actually physically touching the tablet); the child
then pulls back the tablet, corrects the robot's attempt by writing on top of or
next to the robot's writing, and ``sends'' his/her demonstration to the robot by
pressing a small button on the tablet. The robot learns from this demonstration
and tries again. The child continues the turn-taking until they decide to train
the robot on another word. In total, the children performed on average 12.16
($SD=2.61$) rounds of writing (complete details on the rationale and
implementation of this experiment can be found in \redacted).

@@

The experiment was carried out with an Aldebaran {\sc nao} robot, using ROS as a
middleware to build the attention estimation pipeline (Figure~\ref{fig:system}).
Head pose estimation, presented in section~\ref{sec:vfoa}, builds on the {\tt
dlib} and OpenCV libraries; the pose transformations are handled by the ROS {\sc
tf} library. The same {\sc tf} library is used to represent the possible point
of interests as individual frames: an object is considered to be in focus when
its frame lies within the field of attention of the participant
(Figure~\ref{fig:vfoa}).  The implementation is open-source and available at
\redacted.

The implementation of the hand-writing activity itself has been presented by
\redacted.

@@

\redacted

>>>>

\usepackage{xspace}
\newcommand{\eg}{\textit{e.g.}\xspace}
\newcommand{\etal}{\textit{et al.}\xspace}
\newcommand{\ie}{\textit{i.e.}\xspace}
\newcommand{\etc}{\textit{etc.}\xspace}
\newcommand{\vs}{\textit{vs.}\xspace}

@@

\title{From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction}
\author{Séverin Lemaignan \qquad Fernando Garcia \qquad Alexis Jacq \qquad Pierre Dillenbourg\\Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)\\École Polytechnique Fédérale de Lausanne (EPFL)}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{head_pose}
    \caption{The 6D head pose is estimated by fitting a 3D model of an
        adult head (left) onto the detected 2D features of the face (right). We
        rely on an iterative $PnP$ algorithm, using 8 correspondence pairs
        (three are depicted: the sellion -- the nasal depression --, the left
        tragion and the menton). The 3D origin of the head is set at the sellion.}

@@

The experiment, part of the CoWriter project~\cite{Hood:2015}, involves a robot
which tries to engage a child in handwriting tasks using a \emph{learning by
teaching} paradigm (\ie the child is the teacher, and he/she attempts to improve
the robot's handwriting). A tactile tablet is used as writing support.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\columnwidth]{realSetup}
    \caption{\small Picture of the interaction with one of the children.}
    \label{fig:realSetup}
\end{figure}

@@

The interaction is organized in rounds of writing: during a typical round, the
child requests the robot to write something (a single letter, a number, or a
full word), and presents a tactile tablet (equipped with a custom writing
application) to the robot. The robot writes on the tablet by mimicking the
writing gesture (but without actually physically touching the tablet); the child
then pulls back the tablet, corrects the robot's attempt by writing on top of or
next to the robot's writing, and ``sends'' his/her demonstration to the robot by
pressing a small button on the tablet. The robot learns from this demonstration
and tries again. The child continues the turn-taking until they decide to train
the robot on another word. In total, the children performed on average 12.16
($SD=2.61$) rounds of writing (complete details on the rationale and
implementation of this experiment can be found in~\cite{Hood:2015}).

@@

The experiment was carried out with an Aldebaran {\sc nao} robot, using ROS as a
middleware to build the attention estimation pipeline (Figure~\ref{fig:system}).
Head pose estimation, presented in section~\ref{sec:vfoa}, builds on the {\tt
dlib} and OpenCV libraries; the pose transformations are handled by the ROS {\sc
tf} library. The same {\sc tf} library is used to represent the possible point
of interests as individual frames: an object is considered to be in focus when
its frame lies within the field of attention of the participant
(Figure~\ref{fig:vfoa}).  The implementation is open-source and available at
\url{https://github.com/chili-epfl/attention-tracker}.

The implementation of the hand-writing activity itself has been presented by
Hood~\etal in~\cite{Hood:2015}.

@@

This research was partially supported by the Funda\c{c}\~{a}o para a Ci\^{e}ncia
e a Tecnologia (FCT) with reference UID/CEC/ 50021/2013, and by the Swiss
National Science Foundation through the National Centre of Competence in
Research Robotics.
